SIR Model With Testing Flows and Isolation

### 2020-12-08 codes/sir_macpan.Rnw
cleaned up the code

library(directlabels)

# params1 <- read_params("ICU1.csv")
# folder <- system.file("params", package="McMasterPandemic")
# list.files(folder)
# knitr::kable(describe_params(params1))

# knitr::kable(round(t(summary(params1)),2))
# knitr::kable(round(t(get_R0(params1, components=TRUE)),2))
@

<<6: MacPan Params , echo=F>>=
library(zoo)
library(tidyverse)

params <- read_params("ICU1.csv")

@@

pp <- params
## pp <- fix_pars(params, target = c(R0 = sir.R0)) #not sure if I need to update Gbar=6?
# Q? should I update beta0 again? 
state <- make_state(params=pp)
state[] <- 0
state[["S"]] <- 1e6
state[["Im"]] <- 1
# state <- update(state,c(S=sir.params[["N0"]],E=0,Ip=0,Im=0))

>>>>

library(directlabels)
library(zoo)
library(tidyverse)
@

<<6: MacPan Params , echo=F>>=
params <- read_params("ICU1.csv")

@@

pp <- params
## pp <- fix_pars(params, target = c(R0 = sir.R0)) #not sure if I need to update Gbar=6?
state <- make_state(params=pp)
state[] <- 0
state[["S"]] <- 1e6
state[["Im"]] <- 1
